---
title: "Plots for ICML submission"
author: ""
date: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

*Note: for this R Markdown to be compiled properly, the results from the experiments need to be stored in './results/mdc.csv'.*

## Preliminaries
```{r preliminaries, warning=F, message=F,}
library(dplyr)
library(tidyr)
library(ggplot2)
library(latex2exp)


# Clear any existing variables
rm(list = ls())
cbPalette <- rev(c("#000000", "#999999","#E69F00", "#56B4E9",  "#660000", "#CC79A7"))
tau <- 1

save_plots <- FALSE
```

```{r helper_functions, echo=F, warning=F, message=F}
# Define helper functions
bias <- function(tauhat, tau = 1){
  return(abs(mean(tauhat)-tau))
}

sem <- function(x){
  return(sd(x)/(length(x)-1))
}

extract_rows <- function(df_, metric_, config1_, config2_, tau_){
  seeds_set <- seq(0, max(df_$seed), by=1)

  if (tolower(metric_) == "mae") 
  {
    res_mae <- df_ %>%
      filter(seed %in% seeds_set) %>%
      dplyr::select(-c("time", "r", "learning_rate", "n_epochs", "elbo", "epochs",
                       "d_miwae", "sig_prior")) %>%
      group_by(Method, model, n, p, snr, prop_miss, 
               regularize, d, m,
               num_samples_zmul) %>%
      mutate_at(estimators, .funs = funs("mae" =  abs(. - tau))) %>%
      summarise_at(paste(estimators, "mae", sep="_"), funs(mean, sem))
    
  } else if (tolower(metric_) == "mse")
  {
    res_mse <- df_ %>%
      filter(seed %in% seeds_set) %>%
      dplyr::select(-c("time", "r", "learning_rate", "n_epochs", "elbo", "epochs",
                       "d_miwae", "sig_prior")) %>%
      group_by(Method, model, n, p, snr, prop_miss, 
               regularize, d, m,
               num_samples_zmul) %>%
      mutate_at(estimators, .funs = funs("mse" =  (. - tau)^2)) %>%
      summarise_at(paste(estimators, "mse", sep="_"), funs(mean, sem))
  } else if (tolower(metric_) == "bias")
  {
    res_bias <- df_ %>%
      filter(seed %in% seeds_set) %>%
      dplyr::select(-c("time", "r", "learning_rate", "n_epochs", "elbo", "epochs",
                       "d_miwae", "sig_prior")) %>%
      group_by(Method, model, n, p, snr, prop_miss, 
               regularize, d, m,
               num_samples_zmul) %>%
      summarise_at(estimators, .funs = funs("bias" = mean)) %>%
      mutate_at(paste(estimators, "bias", sep="_"), bias)
  }
  
  metric_string <- paste0("res_", tolower(metric_), "$")
  
  condition_str <- paste0(paste(paste(paste(metric_string, names(config1_)[which(sapply(config1_, is.character))], sep=''), 
                                      config1_[which(sapply(config1_, is.character))], sep="=='"),
                                collapse = "' & "), 
                          "'")
  condition_num <- paste(paste(paste(metric_string, names(config1_)[which(sapply(config1_, is.numeric))], sep=''), 
                               config1_[which(sapply(config1_, is.numeric))], sep="=="), collapse = " & ")
  
  condition <- paste0(condition_str, " & ", condition_num, 
                      " & (", metric_string, "m == ", config2_$m , "| is.na(", metric_string, "m))",
                      " & (", metric_string, "num_samples_zmul == ", config2_$num_samples_zmul , 
                      "| is.na(", metric_string, "num_samples_zmul))")
  rows_subset <- which(eval(parse(text = condition)))
  return(list(res = eval(parse(text = paste0("res_", tolower(metric_)))),
              rows_subset = rows_subset,
              seeds_set = seeds_set))
}
```


```{r plot_functions, echo=F, warning=F, message=F}
plot_results <- function(df, metric, config1, config2, tau = 1, xaxis = "n",
                         plot_type = 1, plot_sem = FALSE){
  
  prop_miss_min <- min(df$prop_miss)
  df_tmp <- df %>%
            filter(Method %in% c("Z","X"))
  df <- df %>%
        filter(!(Method %in% c("Z", "X")))
  for (pm in unique(df$prop_miss)){
    tmp <- df_tmp %>%
              mutate(prop_miss=pm)
    df <- data.frame(rbind(df, tmp))
  }
    
  tmp <- extract_rows(df, metric, config1, config2, tau)
  res <- tmp[[1]]
  rows.subset <- tmp[[2]]
  seeds_set <- tmp[[3]]
  if (plot_type == 1){
    df_plot <- res[rows.subset,]
    prop_miss_min <- min(df_plot$prop_miss)
    df_plot <- df_plot %>%
                  filter((Method %in% c("Z", "X") & prop_miss == prop_miss_min) | !(Method %in% c("Z", "X")))
    for (pm in setdiff(unique(df_plot$prop_miss), c(prop_miss_min))){
      tmp <- df_plot %>%
                filter(Method %in% c("Z", "X") & prop_miss == prop_miss_min)
      tmp$prop_miss = pm
      df_plot <- data.frame(rbind(df_plot, tmp))
    }
    p_min <- min(df_plot$p)
    df_plot <- df_plot %>%
                  filter((Method %in% c("Z") & p == p_min) | !(Method %in% c("Z")))
    for (pm in setdiff(unique(df_plot$p), c(p_min))){
      tmp <- df_plot %>%
                filter(Method %in% c("Z") & p == p_min)
      tmp$p = pm
      df_plot <- data.frame(rbind(df_plot, tmp))
    }
    
    if (metric != "bias"){
      plot_dr <- ggplot(data = df_plot) +
        geom_line(aes(x = eval(parse(text = xaxis)), 
                      y = eval(parse(text = paste0("tau_dr_", tolower(metric), "_mean"))), 
                      color = Method,
                      linetype = regularize), size = 1.3)+
        geom_point(aes(x = eval(parse(text = xaxis)), 
                       y = eval(parse(text = paste0("tau_dr_", tolower(metric), "_mean"))), color = Method))+
        facet_wrap(vars(prop_miss)) + 
        ylab(TeX(paste0(metric, '($\\hat{\\tau}_{DR}$)'))) +
        xlab(TeX(paste0('$', xaxis,'$'))) + 
        theme(axis.title = element_text(size = 16, face="bold"),
              axis.text = element_text(size =16),
              legend.position = "top",
              legend.key.size = unit(2.2,"line"),
              legend.text = element_text(size=14, face="bold")) +
        scale_colour_manual(values=cbPalette)
      
      plot_ols <- ggplot(data = df_plot[which(df_plot$Method != "MDC.mi"),]) +         geom_line(aes(x = eval(parse(text = xaxis)), 
                      y = eval(parse(text = paste0("tau_ols_", tolower(metric), "_mean"))), 
                      color = Method,
                      linetype = regularize), size = 1.3)+ 
                  
        geom_point(aes(x = eval(parse(text = xaxis)), 
                       y = eval(parse(text = paste0("tau_ols_", tolower(metric), "_mean"))), color = Method))+
        facet_wrap(vars(prop_miss)) + 
        ylab(TeX(paste0(metric, '($\\hat{\\tau}_{OLS}$)'))) + 
        xlab(TeX(paste0('$',xaxis,'$'))) + 
        theme(axis.title = element_text(size = 16, face="bold"),
              axis.text = element_text(size =16),
              legend.position = "top",
              legend.key.size = unit(2.2,"line"),
              legend.text = element_text(size=14, face="bold")) +
        scale_colour_manual(values=cbPalette[-1])
    } else {
      plot_dr <- ggplot(data = df_plot) +
        geom_line(aes(x = eval(parse(text = xaxis)), 
                      y = eval(parse(text = paste0("tau_dr_", tolower(metric)))), 
                      color = Method,
                      linetype = regularize), size = 1.3)+
        geom_point(aes(x = eval(parse(text = xaxis)), 
                       y = eval(parse(text = paste0("tau_dr_", tolower(metric)))), color = Method))+
        facet_wrap(vars(prop_miss)) + 
        ylab(TeX(paste0(metric, '($\\hat{\\tau}_{DR}$)'))) +
        xlab(TeX(paste0('$', xaxis,'$'))) + 
        theme(axis.title = element_text(size = 16, face="bold"),
              axis.text = element_text(size =16),
              legend.position = "top",
              legend.key.size = unit(2.2,"line"),
              legend.text = element_text(size=14, face="bold")) +
        scale_colour_manual(values=cbPalette)
      
      plot_ols <- ggplot(data = df_plot[which(df_plot$Method != "MDC.mi"),]) +         geom_line(aes(x = eval(parse(text = xaxis)), 
                      y = eval(parse(text = paste0("tau_ols_", tolower(metric)))), 
                      color = Method,
                      linetype = regularize), size = 1.3)+
        geom_point(aes(x = eval(parse(text = xaxis)), 
                       y = eval(parse(text = paste0("tau_ols_", tolower(metric)))), color = Method))+
        facet_wrap(vars(prop_miss)) + 
        ylab(TeX(paste0(metric, '($\\hat{\\tau}_{OLS}$)'))) + 
        xlab(TeX(paste0('$',xaxis,'$'))) + 
        theme(axis.title = element_text(size = 16, face="bold"),
              axis.text = element_text(size =16),
              legend.position = "top",
              legend.key.size = unit(2.2,"line"),
              legend.text = element_text(size=14, face="bold")) +
        scale_colour_manual(values=cbPalette[-1])
    }
    if (plot_sem & (metric != "bias")){
      plot_dr <- plot_dr + 
        geom_errorbar(aes(x=eval(parse(text = xaxis)), 
                          ymin=eval(parse(text = paste0("tau_dr_", tolower(metric), "_mean"))) - 1.96*eval(parse(text = paste0("tau_dr_", tolower(metric), "_sem"))), 
                          ymax=eval(parse(text = paste0("tau_dr_", tolower(metric), "_mean"))) + 1.96*eval(parse(text = paste0("tau_dr_", tolower(metric), "_sem"))),
                          color=Method), 
                      width=0.1)
      
      plot_ols <- plot_ols + 
        geom_errorbar(aes(x=eval(parse(text = xaxis)), 
                          ymin=eval(parse(text = paste0("tau_ols_", tolower(metric), "_mean"))) - 1.96*eval(parse(text = paste0("tau_ols_", tolower(metric), "_sem"))), 
                          ymax=eval(parse(text = paste0("tau_ols_", tolower(metric), "_mean"))) + 1.96*eval(parse(text = paste0("tau_ols_", tolower(metric), "_sem"))),
                          color=Method), 
                      width=0.1)
    }
  } else if (plot_type == 2){
    res$prop_miss <- as.factor(res$prop_miss)
    
    df_plot <- res[rows.subset,]
    df_full <- data.frame(df_plot[which(df_plot$Method %in% c("Z","X")),])
    df_plot <- data.frame(df_plot[which(!(df_plot$Method %in% c("Z", "X"))),])

    duplicates_full <- duplicated(dplyr::select(df_full,
                                                setdiff(parameters,
                                                        c("citcio","seed","time",
                                                          "r", "d_miwae","sig_prior",
                                                          "learning_rate", "n_epochs",
                                                          "elbo","epochs",
                                                          "prop_miss"))))
    df_plot <- rbind(df_plot, df_full[!duplicates_full,])
    
    p_min <- min(df_plot$p)
    df_plot <- df_plot %>%
                  filter((Method %in% c("Z") & p == p_min) | !(Method %in% c("Z")))
    for (pm in setdiff(unique(df_plot$p), c(p_min))){
      tmp <- df_plot %>%
                filter(Method %in% c("Z") & p == p_min)
      tmp$p = pm
      df_plot <- data.frame(rbind(df_plot, tmp))
    }
    
    if (metric != "bias"){
      plot_dr <- ggplot(data = df_plot) +
        geom_line(aes(x = eval(parse(text = xaxis)), 
                      y = eval(parse(text = paste0("tau_dr_", tolower(metric), "_mean"))), 
                      color = Method,
                      linetype = prop_miss), size = 1.3) +
        geom_point(aes(x = eval(parse(text = xaxis)), 
                       y = eval(parse(text = paste0("tau_dr_", tolower(metric), "_mean"))), 
                       color = Method,
                       shape = prop_miss),
                   size = 4.5) + 
        ylab(TeX(paste0(metric, '($\\hat{\\tau}_{DR}$)'))) +
        xlab(TeX(paste0('$', xaxis,'$'))) + 
        theme(axis.title = element_text(size = 16, face="bold"),
              axis.text = element_text(size =16),
              legend.position = "top",
              legend.text = element_text(size=14, face="bold"),
              legend.key.size = unit(2.2,"line")) +
        scale_colour_manual(values=cbPalette)
      
      plot_ols <- ggplot(data = df_plot[which(df_plot$Method != "MDC.mi"),]) +
        geom_line(aes(x = eval(parse(text = xaxis)), 
                      y = eval(parse(text = paste0("tau_ols_", tolower(metric), "_mean"))), 
                      color = Method,
                      linetype = prop_miss), size = 1.3) +
        geom_point(aes(x = eval(parse(text = xaxis)), 
                       y = eval(parse(text = paste0("tau_ols_", tolower(metric), "_mean"))), 
                       color = Method,
                       shape = prop_miss), 
                   size=4.5) + 
        ylab(TeX(paste0(metric, '($\\hat{\\tau}_{OLS}$)'))) +
        xlab(TeX(paste0('$', xaxis,'$'))) + 
        theme(axis.title = element_text(size = 16, face="bold"),
              axis.text = element_text(size =16),
              legend.position = "top",
              legend.text = element_text(size=14, face="bold"),
              legend.key.size = unit(2.2,"line")) +
        scale_colour_manual(values=cbPalette[-1])
    } else{
      plot_dr <- ggplot(data = df_plot) +
        geom_line(aes(x = eval(parse(text = xaxis)), 
                      y = eval(parse(text = paste0("tau_dr_", tolower(metric)))), 
                      color = Method,
                      linetype = prop_miss), size = 1.3)+
        geom_point(aes(x = eval(parse(text = xaxis)), 
                       y = eval(parse(text = paste0("tau_dr_", tolower(metric)))), 
                       color = Method,
                       shape = prop_miss),
                   size = 4.5) + 
        ylab(TeX(paste0(metric, '($\\hat{\\tau}_{DR}$)'))) +
        xlab(TeX(paste0('$', xaxis,'$'))) + 
        theme(axis.title = element_text(size = 16, face="bold"),
              axis.text = element_text(size =16),
              legend.position = "top",
              legend.text = element_text(size=14, face="bold"),
              legend.key.size = unit(2.2,"line")) +
        scale_colour_manual(values=cbPalette)
      
      plot_ols <- ggplot(data = df_plot[which(df_plot$Method != "MDC.mi"),]) +
        geom_line(aes(x = eval(parse(text = xaxis)), 
                      y = eval(parse(text = paste0("tau_ols_", tolower(metric)))), 
                      color = Method,
                      linetype = prop_miss), size = 1.3) + 
        geom_point(aes(x = eval(parse(text = xaxis)), 
                       y = eval(parse(text = paste0("tau_ols_", tolower(metric)))), 
                       color = Method,
                       shape = prop_miss),
                   size=4.5)+ 
        ylab(TeX(paste0(metric, '($\\hat{\\tau}_{OLS}$)'))) +
        xlab(TeX(paste0('$', xaxis,'$'))) + 
        theme(axis.title = element_text(size = 16, face="bold"),
              axis.text = element_text(size = 16),
              legend.position = "top",
              legend.text = element_text(size=14, face="bold"),
              legend.key.size = unit(2.2,"line")) +
        scale_colour_manual(values=cbPalette[-1])
    }
    if (plot_sem & (metric != "bias")){
      plot_dr <- plot_dr + 
        geom_errorbar(aes(x=eval(parse(text = xaxis)), 
                          ymin=eval(parse(text = paste0("tau_dr_", tolower(metric), "_mean"))) - 1.96*eval(parse(text = paste0("tau_dr_", tolower(metric), "_sem"))), 
                          ymax=eval(parse(text = paste0("tau_dr_", tolower(metric), "_mean"))) + 1.96*eval(parse(text = paste0("tau_dr_", tolower(metric), "_sem"))),
                          color=Method), 
                      width=0.1)
      plot_ols <- plot_ols + 
        geom_errorbar(aes(x=eval(parse(text = xaxis)), 
                          ymin=eval(parse(text = paste0("tau_ols_", tolower(metric), "_mean"))) - 1.96*eval(parse(text = paste0("tau_ols_", tolower(metric), "_sem"))), 
                          ymax=eval(parse(text = paste0("tau_ols_", tolower(metric), "_mean"))) + 1.96*eval(parse(text = paste0("tau_ols_", tolower(metric), "_sem"))),
                          color=Method), 
                      width=0.1)
    }
    if (xaxis == "p"){
      plot_dr <- plot_dr + 
        scale_x_continuous(breaks=unique(df_plot$p),
        labels=unique(df_plot$p))
      plot_ols <- plot_ols + 
        scale_x_continuous(breaks=unique(df_plot$p),
        labels=unique(df_plot$p))
    }
    if (xaxis == "log(p)"){
      plot_dr <- plot_dr + 
        scale_x_continuous(breaks=log(unique(df_plot$p)),
        labels=paste0("log(",unique(df_plot$p),")"))
      plot_ols <- plot_ols + 
        scale_x_continuous(breaks=log(unique(df_plot$p)),
        labels=paste0("log(",unique(df_plot$p),")"))
    }
    if (xaxis == "log(n)"){
      plot_dr <- plot_dr + 
        scale_x_continuous(breaks=log(unique(df_plot$n)),
        labels=paste0("log(",unique(df_plot$n),")"))
      plot_ols <- plot_ols + 
        scale_x_continuous(breaks=log(unique(df_plot$n)),
        labels=paste0("log(",unique(df_plot$n),")"))
    }
  }
  return(list(dr=plot_dr, ols=plot_ols))
}


boxplot_results <- function(df, config1, config2, tau = 1){
  
  seeds_set <- seq(0, max(df$seed), by=1)
  
  df_plot <- df %>%
      filter(seed %in% seeds_set) %>%
      dplyr::select(-c("time", "r", "learning_rate", "n_epochs", "elbo",
                "d_miwae", "sig_prior")) 
  
  
  condition_str <- paste0(paste(paste(paste("df_plot$", names(config1)[which(sapply(config1, is.character))], sep=''), 
                                      config1[which(sapply(config1, is.character))], sep="=='"),
                                collapse = "' & "), 
                          "'")
  condition_num <- paste(paste(paste("df_plot$", names(config1)[which(sapply(config1, is.numeric))], sep=''), 
                               config1[which(sapply(config1, is.numeric))], sep="=="), collapse = " & ")
  
  condition <- paste0(condition_str, " & ", condition_num, 
                      " & (df_plot$m == ", config2$m , "| is.na(df_plot$m))",
                      " & (df_plot$num_samples_zmul == ", config2$num_samples_zmul , 
                      "| is.na(df_plot$num_samples_zmul))")
  rows.subset <- which(eval(parse(text = condition)))
  
  df_plot <- df_plot[rows.subset,]
  
  prop_miss_min <- min(df_plot$prop_miss)
  df_tmp <- df_plot %>%
            filter(Method %in% c("Z","X"))
  df_plot <- df_plot %>%
                filter(!(Method %in% c("Z", "X")))
  for (pm in unique(df_plot$prop_miss)){
    tmp <- df_tmp %>%
              mutate(prop_miss=pm)
    df_plot <- data.frame(rbind(df_plot, tmp))
  }

  
  plot_dr <- ggplot(data = df_plot) +
    geom_boxplot(aes(x = Method, 
                     y = tau_dr, 
                     color = Method)) + 
    geom_hline(aes(yintercept = tau)) +
    ylab(TeX('$\\hat{\\tau}_{DR}$')) +
    xlab('') +
    theme(axis.text.x = element_text(face = "bold", 
                                     size = 16, angle = 60, hjust = 1),
          axis.text.y = element_text(size=16),
          axis.title.y = element_text(size = 16, face="bold"),
          legend.position = "none",
          strip.text = element_text(size = 16, face="bold")) +
    scale_colour_manual(values=cbPalette)
  
  plot_ols <- ggplot(data = df_plot[which(df_plot$Method != "MDC.mi"),]) +
    geom_boxplot(aes(x = Method, 
                     y = tau_ols, 
                     color = Method)) + 
    geom_hline(aes(yintercept = tau)) +
    facet_wrap(vars(prop_miss),nrow = 2) + 
    ylab(TeX('$\\hat{\\tau}_{OLS}$')) +
    xlab('') +
    theme(axis.text.x = element_text(face = "bold", 
                                     size = 16, angle = 60, hjust = 1),
          axis.text.y = element_text(size=16),
          axis.title.y = element_text(size = 16, face="bold"),
          legend.position = "none",
          strip.text = element_text(size = 16, face="bold")) +
    scale_colour_manual(values=cbPalette[-1])
  
  if (length(unique(df_plot$snr)) == 1) {
    plot_dr <-  plot_dr + 
                    facet_wrap(vars(prop_miss),nrow = 2)
    plot_ols <-  plot_ols + 
                    facet_wrap(vars(prop_miss),nrow = 2)
  } else {
    plot_dr <-  plot_dr + 
                    facet_wrap(vars(snr, prop_miss),nrow = 2)
    plot_ols <-  plot_ols + 
                    facet_wrap(vars(snr, prop_miss),nrow = 2)
  }
  return(list(dr=plot_dr, ols=plot_ols))
}

```

```{r save_functions, echo=F}
save_all_plots <- function(plots_mse=NULL, plots_mae=NULL, plots_bias=NULL, 
                           configA, configB, path = './figures/'){
  if (!is.null(plots_mse)){
    ggsave(plot=plots_mse$dr, file = paste0('./figures/', 
                paste(paste(names(configA), configA, sep = ''), collapse = '_'),
                '_',
                paste(paste(names(configB), configB, sep = ''), collapse = '_'),
                "_dr_mse.eps"), 
         width=11, height=8.5)
    ggsave(plot=plots_mse$ols, file = paste0('./figures/', 
              paste(paste(names(configA), configA, sep = ''), collapse = '_'),
              '_',
              paste(paste(names(configB), configB, sep = ''), collapse = '_'),
              "_ols_mse.eps"),
       width=11, height=8.5)
  }
  if (!is.null(plots_mae)){
    ggsave(plot=plots_mae$dr, file = paste0('./figures/', 
                paste(paste(names(configA), configA, sep = ''), collapse = '_'),
                '_',
                paste(paste(names(configB), configB, sep = ''), collapse = '_'),
                "_dr_mae.eps"), 
         width=11, height=8.5)
    ggsave(plot=plots_mae$ols, file = paste0('./figures/', 
              paste(paste(names(configA), configA, sep = ''), collapse = '_'),
              '_',
              paste(paste(names(configB), configB, sep = ''), collapse = '_'),
              "_ols_mae.eps"),
           width=11, height=8.5)
  }
  if (!is.null(plots_bias)){
    ggsave(plot=plots_bias$dr, file = paste0('./figures/', 
                  paste(paste(names(configA), configA, sep = ''), collapse = '_'),
                  '_',
                  paste(paste(names(configB), configB, sep = ''), collapse = '_'),
                  "_dr_bias.eps"),
           width=11, height=8.5)
    ggsave(plot=plots_bias$ols, file = paste0('./figures/', 
                  paste(paste(names(configA), configA, sep = ''), collapse = '_'),
                  '_',
                  paste(paste(names(configB), configB, sep = ''), collapse = '_'),
                  "_ols_bias.eps"),
           width=11, height=8.5)
  }
}

save_all_boxplots <- function(boxplots, 
                              configA, configB, path = './figures/'){

  ggsave(boxplots$dr, file = paste0('./figures/', 
                paste(paste(names(configA), configA, sep = ''), collapse = '_'),
                '_',
                paste(paste(names(configB), configB, sep = ''), collapse = '_'),
                "_dr_boxplot.eps"),
         width=11, height=8.5)
  
  ggsave(boxplots$ols, file = paste0('./figures/', 
              paste(paste(names(configA), configA, sep = ''), collapse = '_'),
              '_',
              paste(paste(names(configB), configB, sep = ''), collapse = '_'),
              "_ols_boxplot.eps"),
       width=11, height=8.5)
}

```

## Prepare results

For MDC.mi and MDC.process, we need to extract the results corresponding to the highest ELBO.

```{r, echo=F}
if (!file.exists("./results/mdc_filtered.csv")){
  df_results <- read.csv("./results/mdc.csv", header = TRUE)[,-1]
  parameters <- colnames(df_results)[1:(dim(df_results)[2]-4)]
  estimators <- colnames(df_results)[(dim(df_results)[2]-3):(dim(df_results)[2])]
  

  df_results$tau <- 1
  parameters <- colnames(df_results)[1:(dim(df_results)[2]-5)]
  estimators <- colnames(df_results)[(dim(df_results)[2]-4):(dim(df_results)[2]-1)]
  
  configs <- unique(df_results[,setdiff(parameters, c(estimators, 
                                                      "citcio", "tau", "r", "m",
                                                      "elbo", "time",
                                                      "sig_prior", "d_miwae", "epochs", 
                                                      "n_epochs", "learning_rate"))])
  
  configs[,c("Method", "model", 
             "regularize")] <- apply(configs[,c("Method", "model", 
                                                "regularize")],2, 
                                     as.character)
  
  df_results[,c("Method", "model", 
             "regularize")] <- apply(df_results[,c("Method", "model", 
                                                "regularize")],2, 
                                     as.character)
  
  ############
  # Select MDC results with highest ELBO, 
  # the results for the other methods are simly copied into df_new
  configs <- configs[which(configs$Method %in% c("MDC.mi", "MDC.process")),]
  df_tmp <- df_results[which(df_results$Method %in% c("MDC.mi", "MDC.process")), ]
  df_new_elbo <- df_results[which(!(df_results$Method %in% c("MDC.mi", "MDC.process"))), ]
  
  for (i in 1:dim(configs)[1]){
    if (i%%100 == 0) { 
      print(i)
    }
    conf <- configs[i,]
    condition_na <- ""
    if (is.na(conf$num_samples_zmul)){
      conf <- dplyr::select(conf, -c("num_samples_zmul"))
      condition_na <- " & is.na(df_tmp$num_samples_zmul)"
    }
    condition_str <- paste0(paste(paste(paste("df_tmp$", names(conf)[which(sapply(conf, is.character))], sep=''), 
                                  conf[which(sapply(conf, is.character))], sep="=='"),
                                  collapse = "' & "), 
                            "'")
    condition_num <- paste(paste(paste("df_tmp$", names(conf)[which(sapply(conf, is.numeric))], sep=''), 
                                 conf[which(sapply(conf, is.numeric))], sep="=="), collapse = " & ")
    condition <- paste0(condition_str, " & ", condition_num, condition_na)
    rows.subset <- which(eval(parse(text = condition)))
    tmp_elbo <- df_tmp[rows.subset,] %>%
                  group_by(Method, seed) %>%
                  filter(elbo == max(elbo)) %>% 
                  ungroup() %>%
                  data.frame()
    
    df_new_elbo <- rbind(df_new_elbo, data.frame(tmp_elbo))
    
    # remove current cases from df_tmp data
    df_tmp <- df_tmp[setdiff(1:dim(df_tmp)[1], rows.subset),]
  }
  
  write.csv(df_new_elbo, './results/mdc_filtered.csv')
  df_results <- df_new_elbo
  } else {
  df_results <- read.csv("./results/mdc_filtered.csv", header = TRUE)[,-1]
  df_results <- df_results[which(df_results$n < 1e5),]
  parameters <- colnames(df_results)[1:(dim(df_results)[2]-5)]
  estimators <- colnames(df_results)[(dim(df_results)[2]-4):(dim(df_results)[2]-1)]
  
  configs <- unique(df_results[,setdiff(parameters, c(estimators, "citcio", "tau", "r", "elbo", "time", "seed"))])
  
  configs[,c("Method", "model", 
             "regularize")] <- apply(configs[,c("Method", "model", 
                                                "regularize")],2, 
                                     as.character)
}

```

For the plots, we order the methods in alphabetical order.
```{r reorder_results}
df_results$Method <- as.character(df_results$Method)
df_results <- df_results[sort(df_results$Method,index.return=T)[[2]],]
df_results$Method <- as.factor(df_results$Method)

df_results <- df_results[which(!(df_results$Method == "MDC.process" & !is.na(df_results$num_samples_zmul))),]
```


## Regression adjustment

### Paper

Corresponds to Figure 3 in the paper.

```{r}
configA <- configB <- c()
configA$n <- 10000
configA$p <- 100
configA$d <- 2
configA$snr <- 10
configA$model <- "dlvm"
configA$regularize <- "False"
configB$m <- 20
configB$num_samples_zmul <- 500

configA <- data.frame(configA)
configA$model <- as.character(configA$model)
configA$regularize <- as.character(configA$regularize)
configB <- data.frame(configB)

boxplots <- boxplot_results(df_results[which(df_results$Method != "Mean_imp"),], 
                            configA, configB)

boxplots$ols
```

```{r, echo=F, warning=F}
if (save_plots){
  save_all_boxplots(boxplots, configA, configB)
}
```

Corresponds to Figure 4 in the paper

```{r}
configA <- configB <-  c()
configA$n <- 10000
configA$snr <- 10
configA$d <- 2
configA$model <- "dlvm"
configA$regularize <- "False"
configB$m <- 20
configB$num_samples_zmul <- 500

configA <- data.frame(configA)
configA$model <- as.character(configA$model)
configA$regularize <- as.character(configA$regularize)
configB <- data.frame(configB)

xaxis <- "p"
plot_sem <- F
df <- df_results[which(df_results$p < 1000), ]


plots_mse <- plot_results(df[which(df$Method != "Mean_imp"),], 
                          "mse", configA, configB,
                          xaxis = xaxis,
                          plot_type = 2,
                          plot_sem = plot_sem)

plots_mse$ols
```

```{r, echo=F, warning=F}
if (save_plots){
  save_all_plots(plots_mse, configA=configA, configB=configB)
}
```

### Supplementary material

Corresponds to Figure 1 in the Supplementary Material
```{r}
configA <- configB <-  c()
configA$p <- 100
configA$snr <- 10
configA$d <- 2
configA$model <- "dlvm"
configA$regularize <- "False"
configB$m <- 20
configB$num_samples_zmul <- 500

configA <- data.frame(configA)
configA$model <- as.character(configA$model)
configA$regularize <- as.character(configA$regularize)
configB <- data.frame(configB)

xaxis <- "log(n)"
plot_sem <- F
df <- df_results[which(df_results$p < 1000), ]


plots_mse <- plot_results(df[which(df$Method != "Mean_imp"),], 
                          "mse", configA, configB,
                          xaxis = xaxis,
                          plot_type = 2,
                          plot_sem = plot_sem)

plots_mse$ols
```

```{r, echo=F, warning=F}
if (save_plots){
  save_all_plots(plots_mse, configA=configA, configB=configB)
}
```

Corresponds to Figure 2 in the Supplementary Material
```{r}
configA <- configB <- c()
configA$n <- 10000
configA$p <- 100
configA$d <- 2
configA$snr <- 10
configA$model <- "lrmf"
configA$regularize <- "False"
configB$m <- 20
configB$num_samples_zmul <- 500

configA <- data.frame(configA)
configA$model <- as.character(configA$model)
configA$regularize <- as.character(configA$regularize)
configB <- data.frame(configB)

boxplots <- boxplot_results(df_results[which(df_results$Method != "Mean_imp"),], 
                            configA, configB)

boxplots$ols
```

```{r, echo=F, warning=F}
if (save_plots){
  save_all_boxplots(boxplots, configA, configB)
}
```


## Doubly robust estimation

### Paper

Corresponds to Figure 5 in the paper

```{r}
configA <- configB <- c()
configA$n <- 10000
configA$p <- 1000
configA$d <- 2
configA$snr <- 10
configA$model <- "lrmf"
configA$regularize <- "True"
configB$m <- 20
configB$num_samples_zmul <- 500

configA <- data.frame(configA)
configA$model <- as.character(configA$model)
configA$regularize <- as.character(configA$regularize)
configB <- data.frame(configB)

boxplots <- boxplot_results(df_results[which(df_results$Method != "Mean_imp"),], 
                            configA, configB)

boxplots$dr
```

```{r, echo=F, warning=F}
if (save_plots){
  save_all_boxplots(boxplots, configA, configB)
}
```

Corresponds to Figure 6 in the paper

```{r}
configA <- configB <- c()
configA$n <- 10000
configA$p <- 1000
configA$d <- 2
configA$snr <- 10
configA$model <- "dlvm"
configA$regularize <- "True"
configB$m <- 20
configB$num_samples_zmul <- 500

configA <- data.frame(configA)
configA$model <- as.character(configA$model)
configA$regularize <- as.character(configA$regularize)
configB <- data.frame(configB)

boxplots <- boxplot_results(df_results[which(df_results$Method != "Mean_imp"),], 
                            configA, configB)

boxplots$dr
```

```{r, echo=F, warning=F}
if (save_plots){
  save_all_boxplots(boxplots, configA, configB)
}
```

Corresponds to Figure 7 in the paper
```{r}
configA <- configB <-  c()
configA$n <- 10000
configA$snr <- 10
configA$d <- 2
configA$model <- "dlvm"
configA$regularize <- "True"
configB$m <- 20
configB$num_samples_zmul <- 500

configA <- data.frame(configA)
configA$model <- as.character(configA$model)
configA$regularize <- as.character(configA$regularize)
configB <- data.frame(configB)

xaxis <- "log(p)"
plot_sem <- F

plots_mse <- plot_results(df_results[which(df_results$Method != "Mean_imp"),], 
                          "mse", configA, configB,
                          xaxis = xaxis,
                          plot_type = 2,
                          plot_sem = plot_sem)

plots_mse$dr
```

```{r, echo=F, warning=F}
if (save_plots){
  save_all_plots(plots_mse, configA=configA, configB=configB)
}
```

### Supplementary Material

Corresponds to Figure 3 in the Supplementary Material

```{r}
configA <- configB <-  c()
configA$p <- 1000
configA$snr <- 10
configA$d <- 2
configA$model <- "dlvm"
configA$regularize <- "True"
configB$m <- 20
configB$num_samples_zmul <- 500

configA <- data.frame(configA)
configA$model <- as.character(configA$model)
configA$regularize <- as.character(configA$regularize)
configB <- data.frame(configB)

xaxis <- "log(n)"
plot_sem <- F

plots_mse <- plot_results(df_results[which(df_results$Method != "Mean_imp"),], 
                          "mse", configA, configB,
                          xaxis = xaxis,
                          plot_type = 2,
                          plot_sem = plot_sem)

plots_mse$dr
```

```{r, echo=F, warning=F}
if (save_plots){
  save_all_plots(plots_mse, configA=configA, configB=configB)
}
```